A seamless, client-centric programming model for type safe web applications

### 2014-06-19 paper.tex
Fix garbled sentence on P10

In our solution, this representation is obtained through the use of the \lstinline!remote! function, which when executed on the server pairs a function with a
unique identifier and on the client, and when executed on the client returns
said identifier so that the client may now refer to the function. While this
has the advantage of being simple to implement, one major drawback of this
method is that all functions must be explicitly imported in the \lstinline!App!
monad prior to being called over the network.

>>>>

In our solution, this representation is obtained through the use of the \lstinline!remote! function, which when executed on the server pairs a function with a
unique identifier, and when executed on the client returns
said identifier so that the client may now refer to the function. While this
has the advantage of being simple to implement, one major drawback of this
method is that all functions must be explicitly imported in the \lstinline!App!
monad prior to being called over the network.
